 

### 2020-12-17 docs/index.rmd
mayor-update-paper

---
author: " "
bibliography:
- '../input/bib/zlibrary.bib'
csl:
- '../input/bib/apa6.csl'
title: " "
output:
    html_document:
      number_sections: false
---

>>>>

---
author: " "
bibliography:
- '../input/bib/zlibrary.bib'
csl:
- '../input/bib/apa6.csl'
title: " "
output:
    bookdown::html_document2:
        smart: false
        includes:
          in_header: head_github-activity.html
---
